Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-04-21 main.tex
a few comments/queries

Given a machine trace $\seq{\mach}$ and a call map the identity coloring can be
computed by iterating through the trace:
\begin{enumerate}
\item Start by coloring $\mach_0$ as $\ME$.
\item Color every subsequent state as $\ME$, until the first machine
  state (if any) at which the instruction executed is a
  the beginning of a call sequence.
\item Color the entire call sequence $\TRANS$. This necessarily
  contains a machine state $\mach_c$ which is a $\JAL$.
\item Color every subsequence state as $\NOTME$, until the first state
  $\mach_r$ after $\mach_c$ in the trace (if any) such that the pc of
  $\PC{\mach_r}$ is equal to $\PC{\mach_c} + 4$, and whose stack
  pointer is identical to that of $\mach_c$. Then mark $\mach_r$ as
  $\ME$ and got to step (2).
\end{enumerate}

@@

Given a contour $C$ and a machine state $M$, the {\em contoured trace}
induced by $C$ and $M$, written $\induced{C}{M}$, is the (finite or
infinite) sequence of pairs of (contour, machine state) pairs in which
states in adjacent pairs are related by $\stepstounderfull$, and in which
contours in adjacent pairs are constructed as follows:
\begin{itemize}
\item If in the identity coloring of $\seq{\mach}$ the identity of
  consecutive states is preserved ($\ID_i$ = $\ID_{i+1}$) then
  $C_{i+1} = C_i$.
\item If $\ID_{i} = \ME$ and $\ID_{i+1} = \TRANS$, then $C_{i+1}$ is
  constructed from $C_i$ by setting the local state of $\mach_i$ (the
  caller) to $\HIGHSEC \times \HIGHINT$. The local state is comprised
  of everything below the stack pointer at $\mach_i$.
\item If $\ID_{i} = \TRANS$ and $\ID_{i+1} = \NOTME$, then $C_{i+1}$ is
  constructed from $C_i$ by making the top $n$ locations in the stack,
  where $n$ is the mapping of the transition call sequence in the call map,
  readable and writeable $\LOWSEC \times \LOWINT$.
\item If $\ID_{i} = \TRANS$ and $\ID_{i+1} = \ME$, then $C_{i+1}$ is
  constructed from $C_i$ by setting the local state of the caller
  to $\LOWSEC \times \LOWINT$, and making everything above the stack
  pointer $\HIGHSEC \times \HIGHINT$ again.
\end{itemize}

>>>>

Given a machine trace $\seq{\mach}$ and a call map the identity coloring can be
computed by iterating through the trace:
\begin{enumerate}
\item Start by coloring $\mach_0$ as $\ME$.
\item Color every subsequent state as $\ME$, until the first machine
  state (if any) at which the instruction executed is a
  the beginning of a call sequence.
\item Color the entire call sequence $\TRANS$. This necessarily
  contains a machine state $\mach_c$ which is a $\JAL$.
\item Color every subsequent state as $\NOTME$, until the first state
  $\mach_r$ after $\mach_c$ in the trace (if any) such that the pc of
  $\PC{\mach_r}$ is equal to $\PC{\mach_c} + 4$, and whose stack
  pointer is identical to that of $\mach_c$. Then mark $\mach_r$ as
  $\ME$ and go to step (2).
\end{enumerate}

@@

Given a contour $C$ and a machine state $M$, the {\em contoured trace}
induced by $C$ and $M$, written $\induced{C}{M}$, is the (finite or
infinite) sequence of pairs of (contour, machine state) pairs in which
states in adjacent pairs are related by $\stepstounderfull$, and in which
contours in adjacent pairs are constructed as follows:
\begin{itemize}
\item If in the identity coloring of $\seq{\mach}$ the identity of
  consecutive states is preserved ($\ID_i$ = $\ID_{i+1}$) then
  $C_{i+1} = C_i$.
\item If $\ID_{i} = \ME$ and $\ID_{i+1} = \TRANS$, then $C_{i+1}$ is
  constructed from $C_i$ by setting the local state of $\mach_i$ (the
  caller) to $\HIGHSEC \times \HIGHINT$. The local state is comprised
  of everything below the stack pointer at $\mach_i$.
\item If $\ID_{i} = \TRANS$ and $\ID_{i+1} = \NOTME$, then $C_{i+1}$ is
  constructed from $C_i$ by making the top $n$ locations in the stack,
  where $n$ is the mapping of the transition call sequence in the call map,
  readable and writeable $\LOWSEC \times \LOWINT$.
\item If $\ID_{i} = \TRANS$ \apt {$\NOTME$ ? } and $\ID_{i+1} = \ME$, then $C_{i+1}$ is
  constructed from $C_i$ by setting the local state of the caller
  to $\LOWSEC \times \LOWINT$, and making everything above the stack
  pointer $\HIGHSEC \times \HIGHINT$ again.
\end{itemize}
